DATA 624 Homework 5

### 2020-03-07 DATA624/HW5.Rmd
Additional work on HW5

**This was and interesting exercise.  Some of the more sophisticated approaches preformed less well on the test set than the seasonal naïve model.  In the end the `r rmse_df[rmse_df$RMSE == min(rmse_df$RMSE),]$Model` preformed the best on the test set.**

@@

>>>>

**This was and interesting exercise.  I decided to run it through a buch of models, even some that didn't make sense given this data set.  Some of the more sophisticated approaches preformed less well on the test set than the seasonal naïve model.  In the end the `r rmse_df[rmse_df$RMSE == min(rmse_df$RMSE),]$Model` preformed the best on the test set.**

@@

```{r}
# Window doesn't return a ts object so we need to redefine
retail_train <- ts(as.vector(retail_ts), start=c(1982,4), end=c(2010,12), frequency = 12)
lambda <- BoxCox.lambda(retail_train)
bc_retail_train <- BoxCox(retail_train, lambda = lambda)
stl_retail_train <- stl(bc_retail_train, s.window="periodic") # Guessing on s.window setting based on documentation
stl_time_series <- data.frame(stl_retail_train$time.series)
sa_retail_train <- bc_retail_train - stl_time_series$seasonal

ets_retail_train <- forecast(sa_retail_train)
bc_retail_test <- BoxCox(retail_test, lambda = lambda)
accuracy(ets_retail_train, bc_retail_test)
```
